Earth at night*\\ {\footnotesize \textsuperscript{*}The visualisation of average radiance in specific area}

### 2021-09-20 paper/main.tex
fix compile error

This document is the description about a solution of calculating global night lights to make a visualisation. World Bank Nightime Light Data consists of a lot of satellite imagery 
stored in Amazon Web Services (AWS). Latest files from 2012 to 2020 are generated by the sensor 
named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) \cite{WorldBan13:online}. All of the imagery and metadata is  
stored by Cloud Optimized GeoTIFF (COG) \cite{CloudOpt5:online} format and organized by Spatial Temporal Asset Catalog (STAC) standard \cite{SpatioTe90:online}. 
This project only needs imagery in 3 specific areas. However, it is neccessary to process all of them. 
This project can be a good chance to learn the trend of radiance in these areas. Some researchers also try to find light pollution by this kind of data \cite{BARA2020106658}.

@@

Low Earth Orbit (LEO) (picture ~\ref{LEO}) is the closest orbit to the earth for a satellite. It is only less than 400 kilometers above the surface of the earth, but it may be even higher than 2000 kilometers. Range \cite{WhatisRe36:online}. Such low-orbit operation has inherent advantages for satellites in shooting satellite maps and navigation, etc. \cite{earthdata28:online}. The current high-resolution images are basically taken by it, and such orbits are often used by the International Space Station (ISS) as a common orbit. The design of this orbit makes it easier for astronauts to travel to and from it. The satellite in this orbit moves at a speed of about 7.8 kilometers per second; for a low-orbit satellite, it usually orbits the earth at this speed for only 90 minutes, which means 16 orbits around the earth. It provides good feasibility for the realization of satellite map technology and satellite positioning technology\cite{ESAkerne12: online}.

>>>>

This document is the description of a solution to calculating global night lights to make a visualisation. World Bank Nightime Light Data consists of a lot of satellite imagery 
stored in Amazon Web Services (AWS). Latest files from 2012 to 2020 are generated by the sensor 
named Visible Infrared Imaging Radiometer Suite Day-Night Band (VIIRS DNB) \cite{WorldBan13:online}. All of the imagery and metadata is  
stored by Cloud Optimized GeoTIFF (COG) \cite{CloudOpt5:online} format and organized by Spatial Temporal Asset Catalog (STAC) standard \cite{SpatioTe90:online}. 
This project only needs imagery in 3 specific areas. However, it is necessary to process all of them. 
This project can be a good chance to understand the trend of radiance in these areas. Some researchers also try to find light pollution by this kind of data \cite{BARA2020106658}.

@@

Low Earth Orbit (LEO) (picture ~\ref{LEO}) is the closest orbit to the earth for a satellite. It is only less than 400 kilometers above the surface of the earth, but it may be even higher than 2000 kilometers. Range \cite{WhatisRe36:online}. Such low-orbit operation has inherent advantages for satellites in shooting satellite maps and navigation, etc. \cite{earthdata28:online}. The current high-resolution images are basically taken by it, and such orbits are often used by the International Space Station (ISS) as a common orbit. The design of this orbit makes it easier for astronauts to travel to and from it. The satellite in this orbit moves at a speed of about 7.8 kilometers per second; for a low-orbit satellite, it usually orbits the earth at this speed for only 90 minutes, which means 16 orbits around the earth. It provides good feasibility for the realization of satellite map technology and satellite positioning technology\cite{ESAkerne12:online}.
